An Overview of Distributed Version Control Systems

### 2010-06-26 laarsample.tex
Cambie el final de la introducción para que no use futuro y sea más como todos los demás paper. Agregado el uso de los \ref para crear referencias a secciones

%\input{tcilatex}
\documentstyle[laarstyle,graphicx,fancyhdr]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%TCIDATA{Created=Mon Jun 26 12:16:44 2000}
%TCIDATA{LastRevised=Fri Feb 21 17:20:01 2003}
%TCIDATA{Language=American English}

@@

Most software projects use Version Control Systems (VCS) to manage revisions
of source code. 
Version Control Systems traditionally track the whole history of the
source code in a central server that everyone that can access. 
Users need to access this central server to work with their VCS.
A modern, different approach of doing revision control is using a \emph{Distributed} Version Control System (DVCS).
In these systems, there is no central server that contains the history and tracks changes,
instead everyone has a copy of the full repository with the complete history.
Given the lack of a centralized server they are also called De-centralized Version Control Systems.

As stated in the abstract, we're going to do an overview of DVCS and comparison, based on the DVCS Git. 
First we're going to have a quick look to the history of DVCS. Then there is a review of the overall architecture of DVCS, and then a comparison to centralized version control systems. Some workflows enabled by the use of Distributed Version Control Systems are described, and finally a general evaluation of Git, DVCS in general, and whether it is or not a good idea to switch to them.

\section{DVCS HISTORY}

@@

%----------------------------------------------------------------------
% SECTION II: Architecture
%----------------------------------------------------------------------
\section{ARCHITECTURE}

@@

\section{COMPARISON BETWEEN CENTRALIZED AND DISTRIBUTED}
\subsection{Commits}
In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
Commiting in centralized VCS means ``to share the change with everyone that queries the centralized server'' while in a 
DVCS means to store a change in the history, which is not shared until it's pushed or pulled into another repository.

@@

\section{POSSIBLE WORKFLOWS}

@@

%----------------------------------------------------------------------
% SECTION IV: Then, why should I use it in my project?
%----------------------------------------------------------------------
\section{DVCS COMPARISONS}
There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments. While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN, which is probably the most widely used VCS. 
One key aspect of VCS is its performance. It was said previously in this document that the merging process was crucial for a DVCS because it's something that you'll probably have to do several times during a day in a distributed environment and therefore it should be as fast as possible. This is not the case for all DVCS tools. In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCS.

>>>>

%\input{tcilatex}
%\documentstyle[laarstyle,graphicx,fancyhdr]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%TCIDATA{Created=Mon Jun 26 12:16:44 2000}
%TCIDATA{LastRevised=Fri Feb 21 17:20:01 2003}
%TCIDATA{Language=American English}
\documentclass[a4paper,10pt]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{laarstyle}
\usepackage{xspace}

\newcommand{\sectionReference}[1]{\hspace{-.25em}\ref{#1}\hspace{.5em}}

@@

Most software projects use Version Control Systems (VCS) to manage revisions
of source code. 
Version Control Systems traditionally track the whole history of the
source code in a central server that everyone can access.
Users need to access this central server to work with their VCS.
A modern, different approach of doing revision control is using a \emph{Distributed} Version Control System (DVCS).
In these systems, there is no central server containing the history and tracking changes,
instead of that has a copy of the full repository including the complete history.
Given the lack of a centralized server they are also called De-centralized Version Control Systems.

In section \sectionReference{DVCS HISTORY} there is a small review of DVCS's history. Later, section \sectionReference{ARCHITECTURE} covers
all architecture elements in a DVCS. A comparison between a traditional VCS and the most recent DVCS is done on
section \sectionReference{CENTRALIZED DISTRIBUTED COMPARISON} There is also an enumeration of possible scenarios where using a 
DVCS might be possible and/or useful which are covered on section \sectionReference{WORKFLOWS} Finally, 
section \sectionReference{DVCS COMPARISONS} there is an analysis on different implementation of DVCS system.

\section{DVCS HISTORY}
\label{DVCS HISTORY}

@@

%----------------------------------------------------------------------
% SECTION II: Architecture
%----------------------------------------------------------------------
\section{ARCHITECTURE}
\label{ARCHITECTURE}

@@

\section{COMPARISON BETWEEN CENTRALIZED AND DISTRIBUTED}
\label{CENTRALIZED DISTRIBUTED COMPARISON}

\subsection{Commits}
In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
Commiting in centralized VCS means ``to share the change with everyone that queries the centralized server'' while in a 
DVCS means to store a change in the history, which is not shared until it's pushed or pulled into another repository.

@@

\section{POSSIBLE WORKFLOWS}
\label{WORKFLOWS}

@@

%----------------------------------------------------------------------
% SECTION IV: Then, why should I use it in my project?
%----------------------------------------------------------------------
\section{DVCS COMPARISONS}
\label{DVCS COMPARISONS}

There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments. While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN, which is probably the most widely used VCS. 
One key aspect of VCS is its performance. It was said previously in this document that the merging process was crucial for a DVCS because it's something that you'll probably have to do several times during a day in a distributed environment and therefore it should be as fast as possible. This is not the case for all DVCS tools. In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCS.
